N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
minor fixes

    end
  \end{verbatim}
  We decided against this approach i.e. isolating IO into a separate module,
  because it began to pollute our design's dependency graph with unwanted edges.
  In haskell type class instances exist in an global overloaded name space, that
  takes advantage of haskell's dispatch system. So each data type that is
  implemented for the \texttt{Show} typeclass is able to be printed to StdOut
  \textit{without} carrying around its respective show function. This is not the
  case in SML and it was sorely missed in our implementation. If we were to
  follow the Haskell style of IO (separating impure and pure code explicitly),
  then an IO dependency would be requisite anytime we needed to perform any IO.
  Thus, the IO node would become a dominating node in our dependency graph and
  the import of it into every functor would quickly become unweidly and
  boilerplate. Hence, we chose an SML style design where the structures that are
  mapped upon carry any relevant functions with them to maintain a clean
  decomposition in our design. This type of structure bloat, although
  disgraceful to a haskell programming, seems to be encouraged by SML's module
  system.

>>>>

    end
  \end{verbatim}
  We decided against this approach i.e. isolating IO into a separate module,
  because it began to pollute our design's dependency graph with unwanted edges.
  In haskell, type class instances exist in an global overloaded name space,
  that takes advantage of haskell's dispatch system. So each data type that is
  implemented for the \texttt{Show} typeclass is able to be printed to StdOut
  \textit{without} carrying around its respective show function. This is not the
  case in SML, and it was sorely missed in our implementation. If we were to
  follow the Haskell style of IO (separating impure and pure code explicitly),
  then an IO dependency would be requisite anytime we needed to perform any IO.
  Thus, the IO node would become a dominating node in our dependency graph, and
  the its import into every functor would quickly become boilerplate and
  unweidly. Hence, we chose an SML style design, where the structures that are
  mapped upon carry any relevant functions with them, which maintains a clean
  decomposition in SML. This type of structure bloat, although disgraceful to a
  haskell programming, seems to be encouraged by SML's module system.
